Deterministic Scheduling of Periodic Messages for Cloud RAN

### 2017-07-28 infocom/infocom.tex
avant pull vendredi matin

%\documentclass[a4paper,10pt]{article}
\documentclass[10pt, conference, letterpaper]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{xspace}
\usepackage{url}
\usepackage{graphicx,graphics} 
\usepackage{color}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{longtable}
\usepackage{complexity}
\usepackage{tkz-graph}
\usepackage{float}
\usepackage{tabularx}
\usepackage{setspace}
\usepackage{icomma}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\usepackage{authblk}
% \usepackage{hyperref}

@@

Let us expose briefly our model: the network topology is modeled by a directed weighted graph and a set of paths (routes) from source nodes (RRHs) to target nodes (BBUs). Time is discretized and a unit of time or slot corresponds to the transmission of a minimal unit of data over the network. The process must be  predictable (i.e. the date of arrival of packets is known beforehand). Following LTE standard~\cite{bouguen2012lte}, in this article we assume that the process is periodic. That is, if we look at the network at times $t$ and $t+P$ where $P$ is the period, all messages are at the same position in the network. As we want to avoid any  buffering in internal nodes of the graph. Hence we need to design a periodic process with no collision between messages. To ensure that this property is always true we propose a deterministic process.  We have two sets of values that we can set when building a periodic sending process, called a \emph{periodic assignment} in this article: the time at which each packet is sent by a RRH in each period and the waiting time in the BBU before the answer is sent back to the RRH. When building a periodic assignment, we must take into account the periodicity which makes many scheduling methods unusable. Not only a message must not collide with the other messages sent by the others BBU/RRH in the same period, but also in the previous and following periods. The latency, that is the time between the emission of a message and the complete return of its answer must be minimized. This means that the only buffering we are allowed -- the waiting time before sending back the answer-- must be small, in particular when the route is long. Note that the model is technology agnostic, i.e. it is compatible with an optical network with a fixed packet size.

@@

     The experiment clearly shows that statistical multiplexing does not ensure a minimal latency. 
     The latency is extremely high when the load is high, with a margin of about $10,000$ for the worst $10\%$ which corresponds to half the period, that is $0.5$ms. Even when the network is lightly loaded, $20\%$ of the instances have a margin of more than $2,000$. On the other hand, PMLS finds an assignment with margin $0$ in a highly loaded $97\%$ of the time! 
     For each $1000$ slots of latency we remove from the periodic process, we are able to lengthen the routes of $10$km, which has a huge economic impact.
     We feel that it strongly justifies the use of a deterministic sending scheme for latency critical applications such as our C-RAN motivating problem.

>>>>

%\documentclass[a4paper,10pt]{article}
\documentclass[10pt, conference, letterpaper]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{xspace}
\usepackage{url}
\usepackage{graphicx,graphics} 
\usepackage{color}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{longtable}
\usepackage{complexity}
\usepackage{tkz-graph}
\usepackage{float}
\usepackage{tabularx}
\usepackage{setspace}
\usepackage{icomma}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\usepackage{authblk}
\usepackage{hyperref}

@@

Let us expose briefly our model: the network topology is modeled by a directed weighted graph and a set of paths (routes) from source nodes (RRHs) to target nodes (BBUs). Time is discretized and a unit of time or slot corresponds to the transmission of a minimal unit of data over the network. The process must be  predictable (i.e. the date of arrival of packets is known beforehand). Following LTE standard~\cite{bouguen2012lte}, in this article we assume that the process is periodic. That is, if we look at the network at times $t$ and $t+P$ where $P$ is the period, all messages are at the same position in the network. As we want to avoid any  buffering in internal nodes of the graph. Hence we need to design a periodic process with no collision between messages. To ensure that this property is always true we propose a deterministic process.  We have two sets of values that we can set when building a periodic sending process, called a \emph{periodic assignment} in this article: the time at which each packet is sent by a RRH in each period and the waiting time in the BBU before the answer is sent back to the RRH. When building a periodic assignment, we must take into account the periodicity which makes many scheduling methods unusable. Not only a message must not collide with the other messages sent by the others BBU/RRH in the same period, but also in the previous and following periods. The latency, that is the time between the emission of a message and the complete return of its answer must be minimized. This means that the only buffering we are allowed -- the waiting time before sending back the answer-- must be small, in particular when the route is long. Note that the model is technology agnostic, i.e. it is compatible with an optical network with a fixed packet size.   
\renewcommand{\thefootnote}{\*}
\footnote{\href{https://onedrive.live.com/?authkey=\%21AJIgVoXRuxz1jMU&cid=295858CA35B5113F&id=295858CA35B5113F\%21429&parId=root&o=OneUp}{Please click here to download an extended version with details of mathematical proofs.}}

@@

     The experiment clearly shows that statistical multiplexing does not ensure a minimal latency. 
     The latency is extremely high when the load is high, with a margin of about $10,000$ for the worst $10\%$ which corresponds to half the period, that is $0.5$ms. Even when the network is lightly loaded, $20\%$ of the instances have a margin of more than $2,000$. On the other hand, PMLS finds an assignment with margin $0$ in a highly loaded $97\%$ of the time! 
     For each $1000$ slots of latency we avoid from the periodic process, we are able to lengthen the routes of $10$km, which has a huge economic impact.
     We feel that it strongly justifies the use of a deterministic sending scheme for latency critical applications such as our C-RAN motivating problem.
